### 2012-06-27 inst/examples/cautious.Rmd
cautious loop over possible P

``` {r miscpars, dependson="grid"}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .2
P <- 1
````

@@

Bellman's algorithm to compute the a cautious solution that selects a fraction `P` = `P` of the optimal harvest solution for all possible trajectories in the iterative optimization.

``` {r  find_dp_opt, dependson="SDP_Mat"}
opt <- find_dp_cautious(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=0, P = P)
````

@@

``` {r policyfn_plot, dependson="find_dp_opt"}
q1 <- qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement") + 
geom_point(aes(x,y), data=data.frame(x=opt$S, y=opt$S), col="red")
q1
````

and the value function (at equilibrium):

``` {r valuefn_plot, dependson="find_dp_opt"}
q2 <- qplot(x_grid, opt$V, xlab="stock size", ylab="value") + 
geom_vline(xintercept=opt$S)
q2
````

### Simulate

Now we'll simulate 100 replicates of this stochastic process,
``` {r  simulate, dependson="find_dp_opt" }
sims <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
})
````

## Summarize and plot the results

R makes it easy to work with this big replicate data set.  We make data tidy (melt), fast (data.tables), and nicely labeled.

``` {r  tidy, dependson="simulate"}
dat <- melt(sims, id=names(sims[[1]]))  
dt <- data.table(dat)
setnames(dt, "L1", "reps") # names are nice
````

### Plots

Let's begin by looking at the dynamics of a single replicate. The line shows Reed's S, the level above which the stock should be harvested (where catch should be the difference between stock and S).  To confirm that this policy is being followed, note that harvesting only occurs when the stock is above this line, and harvest is proportional to the amount by which it is above.  Change the replicate `reps==` to see the results from a different replicate.

``` {r  p0, dependson="tidy"}
p0 <- ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_abline(intercept=opt$S, slope = 0) +
  geom_line(aes(time, harvest), col="darkgreen") 
p0
````

This plot summarizes the stock dynamics by visualizing the replicates. Reed's S shown again, along with the dotted line showing the allee threshold, below which the stock will go to zero (unless rescued stochastically).

``` {r  p1, dependson="tidy"}
p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
  geom_abline(intercept=xT, slope = 0, lty=2) 
p1 <- p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
p1
````
``` {r  p2, dependson="tidy"}
p2 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
  geom_abline(intercept=xT, slope = 0, lty=2) 
p2 <- p2 + geom_line(aes(time, harvest, group = reps), alpha = 0.2)
p2
````

``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidy"}
profits <-dt[ , sum(profit), by="reps"] 
ggplot(profits) + geom_histogram(aes(V1)) 
````

## Calculate warning signals

# References

``` {r biblio, echo=FALSE, results="asis"}
knitcitations::bibliography("html")
````

>>>>

``` {r miscpars, dependson="grid"}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .2
P <- .5
````

@@

``` {r beparallel, cache=FALSE}
require(snowfall)
sfInit(parallel=TRUE, cpu=16)
````

Bellman's algorithm to compute the a cautious solution that selects a fraction `P` = `P` of the optimal harvest solution for all possible trajectories in the iterative optimization. Loop over 10 values of P.

``` {r  find_dp_opt, dependson="SDP_Mat"}
P <- seq(0, 1, length.out=10)
opts <- lapply(P, function(P) 
  find_dp_cautious(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                     profit, delta, reward=0, P = P))
````

@@

``` {r policyfn_plot, dependson="find_dp_opt"}
require(reshape2)
policy <- melt(as.data.frame(cbind(stock=x_grid, sapply(opts, function(x) x$D[,1])), id="stock")
ggplot(policy) + geom_lines(aes(stock, value, color=variable))
````
